---
title: "HW2"
author: "Your Name (ID)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
![https://encrypted-tbn0.gstatic.com/images?q=tbn%3AANd9GcSaqNn9FqXNPg1JXOOkAbqZWiAtoANpm_SIypUHQufIUSpgQlTq](https://encrypted-tbn0.gstatic.com/images?q=tbn%3AANd9GcSaqNn9FqXNPg1JXOOkAbqZWiAtoANpm_SIypUHQufIUSpgQlTq)

# Problem 1: Summarize the Iris dataset 

```{r}
str(iris)
#summary()
```
Length  Class   Mode 
     0   NULL   NULL 
# Problem 2:

The sample median of the variable Petail.With is  1.199333 

# Problem 3: Draw a histograms of the Sepal.Length variable

```{r}
hist()
```
---
title: "HW2"
author: "Your Name (ID)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
![https://encrypted-tbn0.gstatic.com/images?q=tbn%3AANd9GcSaqNn9FqXNPg1JXOOkAbqZWiAtoANpm_SIypUHQufIUSpgQlTq](https://encrypted-tbn0.gstatic.com/images?q=tbn%3AANd9GcSaqNn9FqXNPg1JXOOkAbqZWiAtoANpm_SIypUHQufIUSpgQlTq)

# Problem 1: Summarize the Iris dataset 

```{r}
str(iris)
#summary()
```
Length  Class   Mode 
     0   NULL   NULL 
# Problem 2:

The sample median of the variable Petail.With is  1.199333 

# Problem 3: Draw a histograms of the Sepal.Length variable

```{r}
hist()
```
---
title: "HW2"
author: "Your Name (ID)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
![https://encrypted-tbn0.gstatic.com/images?q=tbn%3AANd9GcSaqNn9FqXNPg1JXOOkAbqZWiAtoANpm_SIypUHQufIUSpgQlTq](https://encrypted-tbn0.gstatic.com/images?q=tbn%3AANd9GcSaqNn9FqXNPg1JXOOkAbqZWiAtoANpm_SIypUHQufIUSpgQlTq)

# Problem 1: Summarize the Iris dataset 

```{r}
str(iris)
#summary()
```
Length  Class   Mode 
     0   NULL   NULL 
# Problem 2:

The sample median of the variable Petail.With is  1.199333 

# Problem 3: Draw a histograms of the Sepal.Length variable

```{r}
hist()
```
hist(iris$Sepal.Length)
# Problem 4: Draw a scatter plot 
# Problem 4: Draw a scatter plot 
# Problem 4: Draw a scatter plot 
1
